# Package installation and configuration on Linux
## Author: Lu


```{r global_options, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(eval=FALSE)
```

###  Linux (Ubuntu 14.04)
#### Packages installed to `/path/to/your/Program/`
#### **Two options:**

**1. dump into `/usr/local/bin`**

```{r}
# put in usr/local/bin
cd <path>/to/your/program
sudo cp * /usr/local/bin  
```

**2. add path in `.bashrc`, copy paste the path at the bottom of the file, don't forget to source it!**

```{r}
cd
ls -al
nano .bashrc
export PATH=$PATH:/<path>/to/your/program
#Ctrl+x, save (yes)
source ~/.bashrc
cd ..
```

### [FastQC](http:/www.bioinformatics.babraham.ac.uk/projects/fastqc/)
Need to first make sure java installed, check:
####files can be downloaded using `wget`

```{r}
java --version
# if not installed
sudo apt-get install default-jre
```

Actually installing FastQC is as simple as unzipping the zip file it comes in into a
suitable location.  That's it.  Once unzipped it's ready to go

```{r}
wget http:/www.bioinformatics.babraham.ac.uk/projects/fastqc/fastqc_v0.11.5.zip
unzip fastqc_v0.11.5.zip
cd ./FastQc
chmod 755 fastqc

nano ~/.bashrc
export PATH=$PATH:/path/to/your/Program/FastQC
source ~/.bashrc
```


### [Prinseq](http:/prinseq.sourceforge.net/manual.html)

```{r}
wget https:/sourceforge.net/projects/prinseq/files/standalone/prinseq-lite-0.20.4.tar.gz
tar -zxvf prinseq-lite-0.20.4.tar.gz

sudo cp -puv prinseq-lite-0.20.4/prinseq-lite.pl /usr/local/bin/prinseq-lite && chmod +x /usr/local/bin/prinseq-lite
sudo cp -puv prinseq-lite-0.20.4/prinseq-graphs.pl /usr/local/bin/prinseq-graphs && chmod +x /usr/local/bin/prinseq-graphs
```


### [FASTX_Toolkit](http:/hannonlab.cshl.edu/fastx_toolkit/commandline.html)

**Ved installed it under `/home/bqhs/Bioinformatics` **
```{r}
#wget http:/hannonlab.cshl.edu/fastx_toolkit/fastx_toolkit_0.0.13_binaries_Linux_2.6_amd64.tar.bz2
#tar -xjf fastx_toolkit_0.0.13_binaries_Linux_2.6_amd64.tar.bz2

export PATH=$PATH:/home/bqhs/Bioinformatics/fastx_toolkit

```


### [tophat2](https:/ccb.jhu.edu/software/tophat/manual.shtml)

```{r}
cd /path/to/your/Program
wget https:/ccb.jhu.edu/software/tophat/downloads/tophat-2.1.1.Linux_x86_64.tar.gz
tar -zxvf tophat-2.1.1.Linux_x86_64
nano .bashrc
export PATH=$PATH:/path/to/your/Program/tophat-2.1.1.Linux_x86_64
source ~/.bashrc
cd ..
```


### [bowtie2](http:/bowtie-bio.sourceforge.net/bowtie2/manual.shtml)

```{r}
wget https:/sourceforge.net/projects/bowtie-bio/files/bowtie2/2.2.9/bowtie2-2.2.9-linux-x86_64.zip
unzip bowtie2-2.2.9-linux-x86_64.zip

nano ~/.bashrc
export PATH=$PATH:/path/to/your/Program/bowtie2-2.2.9
source ~/.bashrc
cd ..
```


### [STAR](https:/github.com/alexdobin/STAR)

```{r}
wget https:/github.com/alexdobin/STAR/archive/STAR_2.5.0a.tar.gz
tar -zxvf STAR_2.5.0a.tar.gz
cd STAR-STAR_2.5.0a/source
make STAR

nano ~/.bashrc
export PATH=$PATH:/path/to/your/Program/STAR_2.5.0a/bin/Linux_x86_64
source ~/.bashrc
cd ..
```


### [BWA](http:/bio-bwa.sourceforge.net/bwa.shtml)

```{r}
wget https:/sourceforge.net/projects/bio-bwa/files/bwa-0.7.15.tar.bz2
bunzip2 bwa-0.7.15.tar.bz2
tar -xvf bwa-0.7.15.tar
cd ./bwa-0.7.15m
make 

nano ~/.bashrc
export PATH=$PATH:/path/to/your/Program/bwa-0.7.15
source ~/.bashrc
cd ..
```


### [cufflinks](http:/cole-trapnell-lab.github.io/cufflinks/manual/)

```{r}
wget http:/cole-trapnell-lab.github.io/cufflinks/assets/downloads/cufflinks-2.2.1.Linux_x86_64.tar.gz
tar -zxvf cufflinks-2.2.1.Linux_x86_64.tar.gz

nano ~/.bashrc
export PATH=$PATH:/path/to/your/Program/cufflinks-2.2.1.Linux_x86_64
source ~/.bashrc
cd ..
```


### [samtools](http:/www.htslib.org/doc/samtools.html)

```{r}
wget https:/sourceforge.net/projects/samtools/files/samtools/1.3.1/samtools-1.3.1.tar.bz2
bunzip2 samtools-1.3.1.tar.bz2 
tar -xvf samtools-1.3.1.tar
cd ./samtools-1.3.1
make

nano ~/.bashrc
export PATH=$PATH:/path/to/your/Program/samtools-1.3.1
source ~/.bashrc
cd ..
```


### [bcftools](http:/www.htslib.org/doc/bcftools.html)

```{r}
wget https:/sourceforge.net/projects/samtools/files/samtools/1.3.1/bcftools-1.3.1.tar.bz2
bunzip2 bcftools-1.3.1.tar.bz2
tar -xvf bcftools-1.3.1.tar
cd ./bcftools-1.3.1
make

nano ~/.bashrc
export PATH=$PATH:/path/to/your/Program/bcftools-1.3.1
source ~/.bashrc
cd ..
```


### [bedtools](http:/bedtools.readthedocs.io/en/latest/)

```{r}
wget https:/github.com/arq5x/bedtools2/releases/download/v2.25.0/bedtools-2.25.0.tar.gz
tar -zxvf bedtools-2.25.0.tar.gz
cd ./bedtools2
make

nano ~/.bashrc
export PATH=$PATH:/path/to/your/Program/bedtools2
source ~/.bashrc
```


### [HTSeq](http:/www-huber.embl.de/users/anders/HTSeq/doc/overview.html)

Make sure that you the standard GNU build environment installed, as well as Python together with its development headers and numpy and matplotlib. Users of Ubuntu Linux simply type:

```{r}
sudo apt-get install build-essential python2.7-dev python-numpy python-matplotlib
```

To install HTSeq itself, download the source package from the `HTSeq PyPI` page, unpack the tarball, go into the directory with the unpacked files and type there

```{r}
wget --no-check-certificate https:/pypi.python.org/packages/source/H/HTSeq/HTSeq-0.6.1p1.tar.gz
tar -zxvf HTSeq-0.6.1p1.tar.gz
cd ./HTSeq-0.6.1p1
python setup.py build
sudo python setup.py install
#automatically dump the htseq-count to /usr/local/bin and chmod to 775
cd ..
```

